Cosmic web correlations with the shape, spin and peculiar velocties of dark matter halos

### 2013-11-08 paper/main.tex
updates on the shape alignment

{\bf Contreras et al. (2014)} & T-Web & $0.5-1 \hMpc$ & 
filament &$?$ & $>10^{12}$\hMsun\\
&   & & 
filament &$?$ & $<10^{12}$\hMsun\\
&   & & 
wall & $?$ & all masses\\\hline

@@

\begin{figure*}
\includegraphics[width=0.80\textwidth]{Fig2.pdf}
\caption{Median of $\cos\theta$ quantifying the shape alignment for
  the Vweb (left) and the Tweb (right) at two different grid
  resolutions. In the upper (lower) panels the angle $\theta$ is
  measured between the halo minor (major) axis and the first (third)
  eigenvector.} 
\end{figure*}

>>>>

{\bf Contreras et al. (2014)} & T-Web & $0.5-1 \hMpc$ & 
filament &$++$ & all masses\hMsun\\
&   & & 
wall & $--$ & all masses\\\hline

@@

\begin{figure*}
\includegraphics[width=0.80\textwidth]{Fig2.pdf}
\caption{Median of $\cos\theta$ quantifying the shape alignment for
  the Vweb (left) and the Tweb (right) at two different grid
  resolutions. In the upper (lower) panels the angle $\theta$ is
  measured between the halo minor (major) axis and the first (third)
  eigenvector.\label{fig:shape_alignment}} 
\end{figure*}

The shape alignment shows stronger trends. Figure
\ref{fig:shape_alignment} presents the main results as a function of
halo mass. In this case we characterize the shape by the direction
determined by the major axis.

In the case of the V-web we have a clear anti-alignment with respect
to both first and third eigenvectors for massive halos
$>10^{12}$\hMsun. This implies that a halo is typically perpendicular to 
filaments and lies along the plane defined by a sheet. For low mass
halos $<10^{12}$\hMsun we do not find any correlation with the
cosmic web.

The T-web shows alignment/anti-alignment trends starting at masses of
$10^{10}$\hMsun, two orders of magnitude less than the V-web. In this
case we see an alignment along the first and third eigenvectors. It
means that halos in filamentary environments tend to be aligned with
the filament, while halos in pancake environments are perpendicular to
the sheet.
